Exploratory Data Analysis

### 2019-09-16 hw1/results/Exploratory Data Analysis.Rmd
Updated EDA

To fill the missing in the missing data we will alternate between the two modes (578 and 909)

@@

training <- training %>%
  mutate(TEAM_BATTING_SO  = ifelse(is.na(TEAM_BATTING_SO), sample(c(578, 909), 1), TEAM_BATTING_SO))
```

@@

```{r}
training <- training %>%
  mutate(TEAM_BATTING_SO = -1 * TEAM_BATTING_SO) %>%
  mutate_at(scale, .vars = vars(-TARGET_WINS)) %>%
  mutate(TEAM_BATTING = TEAM_BATTING_H + TEAM_BATTING_2B + TEAM_BATTING_3B + TEAM_BATTING_HR + TEAM_BATTING_BB + TEAM_BATTING_SO)
```

```{r}
training %>%
  mutate(x = TEAM_BATTING) %>%
  plot_me(., "Batting", element_blank(), element_blank())
fit <- lm(TARGET_WINS ~ TEAM_BATTING, training)
summary(fit)
```

This model says that the average baseball team will win about `r round(coef(fit)[1],0)` games.  If their batting is one standard deviation better than the average they will win `r round(coef(fit)[2],0)` more games.

>>>>

To fill the missing in the `r nrow(training[is.na(training$TEAM_BATTING_SO),])` missing data we will alternate between the two modes (578 and 909)

@@

training <- training %>%
  mutate(TEAM_BATTING_SO_flag  = ifelse(is.na(TEAM_BATTING_SO), 1, 0)) %>%
  mutate(TEAM_BATTING_SO  = ifelse(is.na(TEAM_BATTING_SO), sample(c(578, 909), 1), TEAM_BATTING_SO))
```

### Pitching Strike Outs

To fill the the `r nrow(training[is.na(training$TEAM_PITCHING_SO),])` missing values with the mean.

```{r}
training <- training %>%
  mutate(TEAM_PITCHING_SO_flag = ifelse(is.na(TEAM_PITCHING_SO), 1, 0)) %>%
  mutate(TEAM_PITCHING_SO = ifelse(is.na(TEAM_PITCHING_SO), mean(TEAM_PITCHING_SO), TEAM_PITCHING_SO))
```

### Double Plays

To fill the the `r nrow(training[is.na(training$TEAM_FIELDING_DP),])` missing values with the mean.

```{r}
training <- training %>%
  mutate(TEAM_FIELDING_DP_flag = ifelse(is.na(TEAM_FIELDING_DP), 1, 0)) %>%
  mutate(TEAM_PITCHING_SO = ifelse(is.na(TEAM_FIELDING_DP), mean(TEAM_FIELDING_DP), TEAM_FIELDING_DP))
```

@@

```{r}
training <- training %>%
  mutate(TEAM_BATTING_SO = -1 * TEAM_BATTING_SO) %>%
  mutate(TEAM_PITCHING_SO = -1 * TEAM_PITCHING_SO) %>%
  mutate(TEAM_PITCHING_H = -1 * TEAM_PITCHING_H) %>%
  mutate(TEAM_FIELDING_E = -1 * TEAM_FIELDING_E) %>%
  mutate_at(scale, .vars = vars(-TARGET_WINS)) %>%
  #mutate(TEAM_BATTING = TEAM_BATTING_H + TEAM_BATTING_2B + TEAM_BATTING_3B + TEAM_BATTING_HR + TEAM_BATTING_BB + TEAM_BATTING_SO) %>%
  mutate(TEAM_BATTING = TEAM_BATTING_H + TEAM_BATTING_BB + TEAM_BATTING_SO) %>%
  mutate(TEAM_PITCHING = TEAM_PITCHING_BB + TEAM_PITCHING_H + TEAM_PITCHING_HR + TEAM_PITCHING_SO) %>%
  mutate(TEAM_FIELDING = TEAM_FIELDING_DP + TEAM_FIELDING_E)
```

```{r}
training %>%
  mutate(x = TEAM_BATTING) %>%
  plot_me(., "Batting", element_blank(), element_blank())
```

```{r}
training %>%
  mutate(x = TEAM_PITCHING) %>%
  plot_me(., "Pitching", element_blank(), element_blank())
```

```{r}
training %>%
  mutate(x = TEAM_FIELDING) %>%
  plot_me(., "Fielding", element_blank(), element_blank())
```

```{r}
fit <- lm(TARGET_WINS ~ TEAM_BATTING + TEAM_PITCHING + TEAM_FIELDING, training)
summary(fit)
```

This model says that the average baseball team will win about `r round(coef(fit)[1],0)` games.  If their batting is one standard deviation better than the average they will win `r round(coef(fit)[2],0)` more games.  They will win `r round(coef(fit)[3],0)` more games for if their pitching and `r round(coef(fit)[4],0)` if their fielding is better than average.
